---
title: "Results Actin Experiments"
author: "Izar"
date: "30/11/2021"
output: word_document
---

#loading packages and Data 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(knitr)
library(tidyverse)
library("writexl")

#loading Data from Excel sheet for experiment 1 and 2
Exp<-read_excel("C:/Users/Izar Schärf/Desktop/MoBi/Semester_7/BPC-Praktikum/Actin versuch data/_BPC Praktikum Werte.xlsx")
#defining the dataframes of Exp 1 and 2
Exp1 <- Exp[2:17,1:4]
colnames(Exp1) = as.data.frame(Exp[1,1:4])

Exp2 <- Exp[2:9,6:9]
colnames(Exp2) = as.data.frame(Exp[1,6:9])

#Loading what ever the fuck the data for experiment 3 is formatted as, will be converted later on 
Exp3_rotz <- read.csv("C:/Users/Izar Schärf/Desktop/MoBi/Semester_7/BPC-Praktikum/Actin versuch data/SPEXGruppe 6.td")

```

## Results Experiment 1
The first Experiment measured the viscosity of the actin solution  with the metal ball method, the time it takes the metal ball to move through the medium allows us to calculate the viscosity. This measurement was performed across samples which had different times for the actin to polymerize. The end result is a polymerization time to viscosity graph.

```{r, echo = FALSE}
#viscosity:
# K = correlation factor
K = 0.000583

#density of the fluid ~ density of water
pfluid = 1000 #kg/m^3

#density of the sphere
psphere = 7850 #Kg/m^3

#acceleration of gravity
g = 9.81 #m/s^2

#diameter of the tube
dtube = 1.183*10^-3#m

#diameter of the sphere
dsphere = 0.6 *10^-3#m

#inclination of the glass tube
theta <- as.numeric(Exp1$`Winkel [°]`)

#velocity of the sphere
v <- as.numeric(Exp1$`Strecke [cm]`)/ as.numeric( Exp1$`Gemessene Zeit [s]`)
v = v /100


#formula for calculatiung viscosity:
visc<- ((5*pi/42*K*dsphere^2*pfluid*g*sin(theta*pi/180))/v *(psphere-pfluid)/pfluid*(dtube+dsphere)/dsphere)

#Output viscosity and time
visc_df <- as.data.frame(as.vector(Exp1[,1]))
visc_df <- as.data.frame(append(visc_df,as.data.frame(visc)))

#setting the vector of times rather than extracting from visc_df
times_vec <- c(5,10,15,20,30,40,50,60)

#calculatin the averages of viscosities from visc_df
visc_av <- numeric(length(dim(visc_df[1])))
  i = 1
  j= 1
  while(i < dim(visc_df)[1]){

    visc_av[j] <- mean(c(visc_df[i,2],visc_df[i+1,2]) )
  
    j = j +1
    i <- i +2
  }
#creating the sd vector from the values in visc_df
  visc_sd <- numeric(length(dim(visc_df[1])))
  i = 1
  j= 1
  while(i < dim(visc_df)[1]){
     
    visc_sd[j] <- sd(c(visc_df[i,2],visc_df[i+1,2]),na.rm = TRUE)
  
    j = j +1
    i <- i +2
  }
visc_plot_data <- data.frame(c(times_vec),c(visc_av),c(visc_sd))

#setting colnames of data for viscosty plot
colnames(visc_plot_data) <-c("Zeit","visc","sd")


#line plot of data
visc_plot1 <-ggplot(visc_plot_data, aes(x = Zeit, y = visc))+
              geom_line(stat="identity", color="black")+
              geom_errorbar(aes(ymin =visc-sd, ymax = visc +sd),width=.2)+
  geom_point()+
              labs(title = "Rolling ball experiment 1", x = "time to set [min]", y = "viscosity [Kg/(m*s)]")

show(visc_plot1)


```

## Results Experiemt 2

In the second experiment the viscosity of solutions with different concentrations of actin (1.0, 2.5, 4.0 µM) was measured after a polymerization time of 60 min, at an angle of 60°. The density was calculated from the given concentrations, the other parameters were the same as in Experiment 1.

```{r, echo=FALSE}
#inclination of the glass tube
theta2 <- as.numeric(Exp2$`Winkel [°]`)

#velocity of the sphere
v2 <- as.numeric(Exp2$`Strecke [cm]`)/ as.numeric( Exp2$`Gemessene Zeit [s]`)
v2 = v2 /100

#formula for calculatiung viscosity:
visc_exp2<- ((5*pi/42*K*dsphere^2*density*g*sin(theta2*pi/180))/v2 *(psphere-pfluid)/density*(dtube+dsphere)/dsphere)

#setting the vector of times rather than extracting from visc_df
conc_vec <- c(unique(concentrations))

#dataframe for concentration vs viscosity
visc_df2 <- data.frame(concentrations,visc_exp2)


#calculatin the averages of viscosities from visc_df
visc_av2 <- numeric(length(dim(visc_df2)[1]))
  i = 1
  j= 1
  while(i < dim(visc_df2)[1]){

    visc_av2[j] <- mean(c(visc_df2[i,2],visc_df2[i+1,2]) )
  
    j = j +1
    i <- i +2
  }
#creating the sd vector from the values in visc_df
  visc_sd2 <- numeric(length(dim(visc_df2)[1]))
  i = 1
  j= 1
  while(i < dim(visc_df2)[1]){
     
    visc_sd2[j] <- sd(c(visc_df2[i,2],visc_df2[i+1,2]),na.rm = TRUE)
  
    j = j +1
    i <- i +2
  }

#defining the data for the plot  
visc_plot_data2 <- data.frame(c(conc_vec),c(visc_av2),c(visc_sd2))

#setting colnames of data for viscosty plot
colnames(visc_plot_data2) <-c("conc","visc","sd")

#line plot of data
visc_plot1 <-ggplot(visc_plot_data2, aes(x = conc, y = visc))+
              geom_line(stat="identity", color="black")+
              geom_errorbar(aes(ymin =visc-sd, ymax = visc +sd),width=.2)+
  geom_point()+
              labs(title = "Rolling ball experiment 2", x = "Concentration [µM]", y = "viscosity [k/(m*s)]")

show(visc_plot1)

```

## Results Experiment 3

The third experiment recorded the flouresscence form the polymerizing Act G + Act NBD.  

```{r, echo = FALSE}

Exp3_clean <- Exp3_rotz[37:nrow(Exp3_rotz),]

Exp3_sep_str <- as.numeric(unlist(strsplit(as.vector(Exp3_clean), split = c("\t"))),na.rm = TRUE)

Time3 <-as.vector(Exp3_sep_str[seq(from = 1, to = length(Exp3_sep_str), by =2)])

Flourescence3 <-as.vector(Exp3_sep_str[seq(from = 2, to = length(Exp3_sep_str), by =2)])

Exp3_data <- data.frame(Time3,Flourescence3) 

Flou_plot1 <-ggplot(Exp3_data, aes(x = Time3, y = Flourescence3))+
           geom_point(size = 0.01)+
  labs(title = "Flourescence labeled polymerization", x = "Time[s]", y = "Flourescence Intensity")+
  ylim(0,110)

show(Flou_plot1)



#Exporting Data as Excel Files
#EXP 1
write_xlsx(visc_plot_data,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_plot_data_exp1.xlsx")

write_xlsx(visc_df,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_df_exp1.xlsx")

#Exp2

write_xlsx(visc_plot_data2,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_plot_data_exp2.xlsx")

write_xlsx(visc_df2,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_df2_exp2.xlsx")

#Exp3

write_xlsx(Exp3_data,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\Flourescenz.xlsx")




```






