---
title: "Results Actin Experiments"
author: "Izar"
date: "30/11/2021"
output: word_document
---



"To do:
--Write Discussion
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(knitr)
library(tidyverse)
library("writexl")
Exp<-read_excel("C:/Users/Izar Schärf/Desktop/MoBi/Semester_7/BPC-Praktikum/Actin versuch data/_BPC Praktikum Werte.xlsx")
#defining the dataframes
Exp1 <- Exp[2:17,1:4]
colnames(Exp1) = as.data.frame(Exp[1,1:4])

Exp2 <- Exp[2:9,6:9]
colnames(Exp2) = as.data.frame(Exp[1,6:9])
```

## Results Experiment 1
The first Experiment measured the viscosity of the actin solution  with the metal ball method, the time it takes the metal ball to move through the medium allows us to calculate the viscosity. This measurement was performed across samples which had different times for the actin to polymerize. The end result is a polymerization time to viscosity graph. 
The desity of the material was determined by measuring the absorbtion at 290 nm with an optical path length of 1 cm and a absorbtivity of  0.63 ±0.01 ml mg^-1
cm^-1, this yielded a absorbtion of 0.562 . 

```{r, echo = FALSE}
#viscosity:
# K = correlation factor
K = 0.000583

#density of the fluid ~ density of water
pfluid = 1000 #kg/m^3

#density of the sphere
psphere = 7850 #Kg/m^3

#acceleration of gravity
g = 9.81 #m/s^2

#diameter of the tube
dtube = 1.183*10^-3#m

#diameter of the sphere
dsphere = 0.6 *10^-3#m

#inclination of the glass tube
theta <- as.numeric(Exp1$`Winkel [°]`)

#velocity of the sphere
v <- as.numeric(Exp1$`Strecke [cm]`)/ as.numeric( Exp1$`Gemessene Zeit [s]`)
v = v /100


#formula for calculatiung viscosity:
visc<- ((5*pi/42*K*dsphere^2*pfluid*g*sin(theta*pi/180))/v *(psphere-pfluid)/pfluid*(dtube+dsphere)/dsphere)

#Output viscosity and time
visc_df <- as.data.frame(as.vector(Exp1[,1]))
visc_df <- as.data.frame(append(visc_df,as.data.frame(visc)))

#setting the vector of times rather than extracting from visc_df
times_vec <- c(5,10,15,20,30,40,50,60)

#calculatin the averages of viscosities from visc_df
visc_av <- numeric(length(dim(visc_df[1])))
  i = 1
  j= 1
  while(i < dim(visc_df)[1]){

    visc_av[j] <- mean(c(visc_df[i,2],visc_df[i+1,2]) )
  
    j = j +1
    i <- i +2
  }
#creating the sd vector from the values in visc_df
  visc_sd <- numeric(length(dim(visc_df[1])))
  i = 1
  j= 1
  while(i < dim(visc_df)[1]){
     
    visc_sd[j] <- sd(c(visc_df[i,2],visc_df[i+1,2]),na.rm = TRUE)
  
    j = j +1
    i <- i +2
  }
visc_plot_data <- data.frame(c(times_vec),c(visc_av),c(visc_sd))

#setting colnames of data for viscosty plot
colnames(visc_plot_data) <-c("Zeit","visc","sd")


#line plot of data
visc_plot1 <-ggplot(visc_plot_data, aes(x = Zeit, y = visc))+
              geom_line(stat="identity", color="black")+
              geom_errorbar(aes(ymin =visc-sd, ymax = visc +sd),width=.2)+
  geom_point()+
              labs(title = "Rolling ball experiment 1", x = "time to set [min]", y = "viscosity [Kg/(m*s)]")



#kable(visc_df) #, digits = c(1,50,50))

#kable(visc_plot_data) #, digits = c(1,50,50))


show(visc_plot1)


```

## Results Experiemt 2

In the second experiment the viscosity of solutions with different concentrations of actin (1.0, 2.5, 4.0 µM) was measured after a polymerization time of 60 min, at an angle of 60°. The density was calculated from the given concentrations, the other parameters were the same as in Experiment 1.

```{r, echo=FALSE}
#inclination of the glass tube
theta2 <- as.numeric(Exp2$`Winkel [°]`)

#velocity of the sphere
v2 <- as.numeric(Exp2$`Strecke [cm]`)/ as.numeric( Exp2$`Gemessene Zeit [s]`)
v2 = v2 /100

#formula for calculatiung viscosity:
visc_exp2<- ((5*pi/42*K*dsphere^2*density*g*sin(theta2*pi/180))/v2 *(psphere-pfluid)/density*(dtube+dsphere)/dsphere)

#setting the vector of times rather than extracting from visc_df
conc_vec <- c(unique(concentrations))

#dataframe for concentration vs viscosity
visc_df2 <- data.frame(concentrations,visc_exp2)


#calculatin the averages of viscosities from visc_df
visc_av2 <- numeric(length(dim(visc_df2)[1]))
  i = 1
  j= 1
  while(i < dim(visc_df2)[1]){

    visc_av2[j] <- mean(c(visc_df2[i,2],visc_df2[i+1,2]) )
  
    j = j +1
    i <- i +2
  }
#creating the sd vector from the values in visc_df
  visc_sd2 <- numeric(length(dim(visc_df2)[1]))
  i = 1
  j= 1
  while(i < dim(visc_df2)[1]){
     
    visc_sd2[j] <- sd(c(visc_df2[i,2],visc_df2[i+1,2]),na.rm = TRUE)
  
    j = j +1
    i <- i +2
  }

#defining the data for the plot  
visc_plot_data2 <- data.frame(c(conc_vec),c(visc_av2),c(visc_sd2))

#setting colnames of data for viscosty plot
colnames(visc_plot_data2) <-c("conc","visc","sd")

#line plot of data
visc_plot1 <-ggplot(visc_plot_data2, aes(x = conc, y = visc))+
              geom_line(stat="identity", color="black")+
              geom_errorbar(aes(ymin =visc-sd, ymax = visc +sd),width=.2)+
  geom_point()+
              labs(title = "Rolling ball experiment 2", x = "Concentration [µM]", y = "viscosity [k/(m*s)]")

show(visc_plot1)

```

## Results Experiment 3

The third experiment recorded the flouresscence form the polymerizing Act G + Act NBD.  

```{r, echo = FALSE}

Exp3_rotz <- read.csv("C:/Users/Izar Schärf/Desktop/MoBi/Semester_7/BPC-Praktikum/Actin versuch data/SPEXGruppe 6.td")

# https://r4ds.had.co.nz/strings.html
Exp3_clean <- Exp3_rotz[37:nrow(Exp3_rotz),]

Exp3_sep_str <- as.numeric(unlist(strsplit(as.vector(Exp3_clean), split = c("\t"))),na.rm = TRUE)

Time3 <-as.vector(Exp3_sep_str[seq(from = 1, to = length(Exp3_sep_str), by =2)])

Flourescence3 <-as.vector(Exp3_sep_str[seq(from = 2, to = length(Exp3_sep_str), by =2)])

Exp3_data <- data.frame(Time3,Flourescence3) 

Flou_plot1 <-ggplot(Exp3_data, aes(x = Time3, y = Flourescence3))+
           geom_point(size = 0.01)+
  labs(title = "Flourescence labeled polymerization", x = "Time[s]", y = "Flourescence Intensity")+
  ylim(0,110)

show(Flou_plot1)

#EXP 1
write_xlsx(visc_plot_data,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_plot_data_exp1.xlsx")

write_xlsx(visc_df,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_df_exp1.xlsx")

#Exp2

write_xlsx(visc_plot_data2,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_plot_data_exp2.xlsx")

write_xlsx(visc_df2,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\visc_df2_exp2.xlsx")

#Exp3

write_xlsx(Exp3_data,"C:\\Users\\Izar Schärf\\Desktop\\MoBi\\Semester_7\\BPC-Praktikum\\Actin versuch data\\Flourescenz.xlsx")




```

## Discussion:

As gathered in the first experiemnt, seen in figure 1, examining the relationship between time to polymerize and viscosity at a constant concentration of Actin G monomers in solution, the viscosity peaks at 50 min of polymerization time. The solution starts gaining viscosity at a linear pace from 20 min to 40 min at which point the rate of increase of viscosity by time to set decreases rapidly until the rate of viscosity gain by time is negative between the measurements at 50 min and 60 min. This suggests that there is a ciritcal concentration of seed actin polymers which will initiate a steady growth phase for the actin polymers, this corrolates with the viscosity because longer polymers induce higher viscosity. The drop in Viscosity at 60 mins time is would not agree with the standart rate of formation models for actin, however a drop in the amount of available ATP which is used in the polymerisation means that after a certain time the rate of formation will no longer be greater than the rate of dissociation.

Regarding figure 2, the clear trend towards higher viscosity at higher actin concentrations can be seen. The curve increases almost as an exp function gathering here from that it is the number of interactions that increase in an exponential combination like way which results in small changes in concentration leading to large changes in viscosity.






